---
title: 'Rwavelet Vignette'
author: "Christophe Chesneau and Fabien Navarro"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    theme: cerulean
    number_sections: yes
    toc: yes
    toc_depth: 5
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Rwavelet Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---
<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 18px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 15px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

```{r, echo=FALSE}
#options(vignetteDocumentFormat=rmarkdown::all_output_formats("rwaveletvignette.Rmd"))
```

```{r Setup, include=FALSE}
library(rwavelet)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=5,
  fig.height=5, 
  fig.align="center"
)
set.seed(0)
library(rwavelet)
par(mgp = c(2,0.5,0),
    mar = c(4,3,2,1),
    oma = c(1,1,0,0))
```

# 1d examples
## Load and plot a signal from the MakeSignal function {#example1}
```{r, echo=TRUE}
J <- 10; n <- 2^J; t <- (1:n) / n
name <- c('Bumps')
f <- MakeSignal(name, n)
plot(t, f, xlab="t", ylab="f(t)",
     type='l', lwd=1.2, main=name)
```

## Plot a noisy version of the original function {#example2}
```{r, echo=TRUE}
SNR <- 4
set.seed(1)
ssig <- sd(f)
sigma <- ssig / SNR
y <- f + rnorm(n, mean=0, sd=sigma)
plot(t, y, xlab="t", ylab="y", main=paste("Noisy", name))
```

## Forward Wavelet Transform (periodized, orthogonal) {#example3}
```{r, echo=TRUE}
qmf <- MakeONFilter('Daubechies', 10)
L <- 3
wc <- FWT_PO(y, L, qmf)
wcf <- FWT_PO(f, L, qmf)
```

## Spike-plot display of wavelet coefficients {#example4}
```{r, echo=TRUE}
PlotWaveCoeff(wc, L, 0.5)
title("Noisy Wavelet Coefs")
PlotWaveCoeff(wcf, L, 0.5)
title("Original Wavelet Coefs")
```

## Universal hard thresholding  {#example5}
```{r, echo=TRUE}
# estimate sigma using the maximum absolute deviation
# using only the fine scale of wc
hatsigma <- MAD(wc[(2^(J-1)+1):2^J])
thr <- sqrt(2*log(length(y)))*hatsigma
# apply hard thresholding 
wc[(2^(L)+1):n] <- HardThresh(wc[(2^(L)+1):n], thr)
# plot the resulting coeficients estimates
PlotWaveCoeff(wc, L, 0.5)
title("Estimated Wavelet Coefs")
fest <- IWT_PO(wc, L, qmf)
snrout <- SNR(f, fest)
plot(t, fest, type='l', lwd=1.4, col='red', xlab="t", ylab="hat_f(t)",
	   main=format(round(snrout,2), nsmall=2))
matlines(t, f, type='l', lty=2)
```

# 2d examples
## Load and plot an image

```{r, echo=TRUE, message=FALSE}
library(imager)
name <- '../inst/extdata/lena.png'
f <- load.image(name)
plot(f, axes=F, interpolate=F, xlab="", ylab="")
```

## Plot a noisy version of the original image
```{r, echo=TRUE, message=FALSE}
ssig <- sd(f)
sdnoise <- ssig/SNR
y <- f + rnorm(ncol(f)*nrow(f), mean=0, sd=sdnoise)
snrin <- SNR(f,y)
plot(y, axes=F, interpolate=F, xlab="", ylab="",
     main=format(round(snrin,2), nsmall = 2))
```

## Image denoising using hard thresholding
```{r, echo=TRUE, message=FALSE}
wc <- FWT2_PO(as.array(squeeze(y)), L, qmf)
thr <- 3*sdnoise
aT <- wc*(abs(wc)>thr)
fest <- IWT2_PO(aT, L, qmf)
snrout <- SNR(f, fest)
plot(as.cimg(fest), axes=FALSE, xlab="", ylab="",
     main=format(round(snrout,2), nsmall=2))
```
